\documentclass{bilidoc}

\geometry{
  a4paper,%
  left = 1.5cm,%
  right = 1.5cm,%
  top = 2.0cm,%
  bottom = 2.0cm%
}%



\usepackage{ulem}

\title{\textbf{\href{https://ascelibrary.org/doi/10.1061/(ASCE)GT.1943-5606.0002314}{Data Compilation from Large Drained Compression Triaxial Tests on Coarse Crushable Rockfill Materials 粗碎石料的大型排水三轴压缩试验数据汇编}}}

\author{Carlos Ovalle \thanks{
    Assistant Professor, Dept. of Civil, Geological and Mining Engineering, Polytechnique Montreal, 2900 Edouard Montpetit Blvd., Montreal, QC, Canada H3T1J4; Research Institute of Mining and Environment, RIME UQAT-Polytechnique, 2900 Edouard Montpetit Blvd., Montreal, QC, Canada H3T1J4 (corresponding author). ORCID: \url{https://orcid.org/000-0002-9648-5262}. Email: \url{carlos.ovalle@polymtl.ca}.
} \and Sandra Linero \thanks{
    Principal Geotechnical Engineer, SRK Consulting (Australasia) Pty Ltd., Level 17, 44 Market St., Sydney, NSW 2000, Australia.
} \and Christophe Dano \thanks{
    Associate Professor, Centre National de la Recherche Scientifique, Institut National Polytechnique, Univ. Grenoble–Alpes, 3SR, 1270 rue de la piscine, Domaine Universitaire, Grenoble 38000, France.
} \and Edgar Bard \thanks{
    Senior Mine Waste Consultant, Golder Associates, 181 Magdalena, Las Condes 7550055, Chile.
} \and Pierre-Yves Hicher \thanks{
    Emeritus Professor, Centre National de la Recherche Scientifique, Unité Mixte de Recherche, Ecole Centrale de Nantes, 1 Rue de la Noë, Nantes 44300, France. 
}\and Rodrigo Osses \thanks{
    Ph.D. Candidate, Dept. of Structural and Geotechnical Engineering, Pontificia Universidad Cat´olica de Chile, 4860 Av. Vicu˜na Mackenna, Macul 7820436, Chile; Facultad de Ingeniería y Ciencias, Departamento de Ingeniería de Obras Civiles, Universidad de La Frontera, 1145 Francisco Salazar, Temuco 4811230, Chile.
} \thanks{
    Note. This manuscript was submitted on August 30, 2019; approved on March 18, 2020; published online on June 27, 2020. Discussion period open until November 27, 2020; separate discussions must be submitted for individual papers. This technical note is part of the {\em\bfseries Journal of Geotechnical and Geoenvironmental Engineering}, © ASCE, ISSN 1090-0241.
}}

\date{}

\begin{document}

\maketitle

\vspace{-7mm}

\begin{Abstract}{Rockfill; Large triaxial tests; Particle crushing; Shear strength; Secant stiffness.}{碎石；大型三轴试验；颗粒破碎；剪切强度；割线刚度。}

    Investigating the mechanical properties of rockfills requires laborious, time-consuming, and expensive large-scale testing. Therefore, practitioners frequently adopt design parameters based on a limited number of reports with experimental results. With the aim of enlarging and consolidating the database on the mechanical behavior of coarse rockfills, this paper compiles 158 drained triaxial compression tests conducted on 33 different materials, performed on samples∼1 m in diameter and having a maximum particle size between 100and 200mm. Data are analyzed in terms of particle breakage, shear strength, and stiffness. The results are compared with limits for high and low shear strength previously reported. At confining pressures lower than 0.2 MPa, rockfills consistently have a maximum internal friction angle higher than 45°; at high pressure, this value decreases to a range between 30° and 40°, mainly due to degradation caused by particle breakage. Average secant Young’s moduli for all uniform and well-graded rockfills analyzed are in the typical range for loose sands, characterized by a normalized secant modulus of 100 to 200. 

    \switchcolumn

    研究碎石的机械性能一般需要费力，费时且昂贵的大规模试验。 因此，从业人员经常根据数量有限的报告和实验结果选用设计参数。为了扩大和巩固有关粗碎石料力学性能的数据库，本文汇编了对33种不同材料进行的158次排水三轴压缩试验，这些试验的样本直径约为1米，其最大粒径在100到200毫米之间。然后我们根据颗粒破损程度，剪切强度和刚度来分析试验数据。将结果与先前报道的高和低剪切强度极限进行比较。 在围压低于0.2MPa的情况下，碎石料的最大内摩擦角始终大于45°。在高压下，该值减小到30°至40°之间，这主要是由于颗粒破裂引起的土块降解。对于所有分析的均匀且分级良好的碎石料，平均正割杨氏模量都在松散砂体的典型范围内，其特征是正割杨氏模量在100到200之间。
    
\end{Abstract}

\input{sections/introduction.tex}
\input{sections/recent-experimental-data-include-in-the-database.tex}
\input{sections/quartzitic-sands-and-ballast-data-collected.tex}
\input{sections/analysis-and-discussion.tex}
\input{sections/conclusions.tex}
\input{sections/data-availability-statement-and-acknowledgements.tex}

\bibliographystyle{plainnat}
\bibliography{Ovalle2020.bib}
    
\end{document}